---
title: "GNU Make part"
author: "Mateusz Lewicki"
date:  "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document: 
    theme: united
    highlight: pygments
    toc: yes
    css: blocks.css
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, inlcude=FALSE, echo=FALSE}
dump_file_cont <- function(type, file){
  return(cat(paste(paste("```",type,sep=""), paste(readLines(file), collapse="\n"), "```", sep="\n")))
}
```
# Puprouse of using GNU Make

GNU Make is a tool which controls the generation of executables and other non-source files of a program from the program's source files.

Make gets its knowledge of how to build your program from a file called the makefile, which lists each of the non-source files and how to compute it from other files. When you write a program, you should write a makefile for it, so that it is possible to use Make to build and install the program.

We can also say that GNU Make is a some kind of pipeline and can be use with conjunction with other pipeline as in Azure, Jenkins,  AWS, Gitlab with specifing a target for every stage.

You can find more about GNU Make Here:

- <https://www.gnu.org/software/make/>
- <https://www.gnu.org/software/make/manual/make.html>
- <https://makefiletutorial.com/>
- <https://www.cl.cam.ac.uk/teaching/0910/UnixTools/make.pdf>

## Brief overwiew of GNU Make in current project

Makefiles are described with `targets`, `dependencies` and `actions`.

In current project there are 4 Makefiles 1 - main and other 3 for building docker images

## Makefile
```{r echo=FALSE, warning=FALSE, inlcude=FALSE, results='asis'}
dump_file_cont("makefile", "../Makefile")
```
::: INFO
>This is [GNU Make Makefile](https://www.gnu.org/software/make/) with usage of [docker](https://docs.docker.com/engine/) and [terraform](https://www.terraform.io/docs/index.html) cli tools.
:::
::: CODE_DESCIPTION
### Overwiew
####  **`deploy: build_images`**
> First targe, whcih will be used when `make` command will be used without parameters or `make deploy` direclty.  
> This target is rewuairng to execute `build_images` target first 
> Here is only one script `cd terraform; terraform apply -auto-approve` wchich is going inside terraform folder and executing `terraform apply` command

####  **`plan:`**
> Script similar as above but here we are only exeuting `terraform plan` command

####  **`build_images: build_apache build_mysql build_lb`**
> Auxilary target which is invoking other targets

####  **`build_apache:`**
####  **`build_mysql:`**
####  **`build_lb:`**
> Three targets for building the docekr images using `docker build` command, tag the container and push it to repositroy (in this case localhost)

####  **`.PHONY: clean`**
> Directive to not save state and execute target `clean` every time (even if was executet moment ago)

####  **`clean:`**
> target for destroing the environment using `terraform destroy` command
:::

## loadbalancer/Makefile
```{r echo=FALSE, warning=FALSE, inlcude=FALSE, results='asis'}
dump_file_cont("makefile", "../images/loadbalancer/Makefile")
```
::: INFO
>This is [GNU Make Makefile](https://www.gnu.org/software/make/) with usage of [sh](https://www.unix.com/man-page/linux/1/sh/) inside [alpine linux](https://wiki.alpinelinux.org/wiki/Main_Page).
:::

### Overwiew

####  **`publish:`**

####  **`dev: no_daemon add_dev_stats`**

####  **`install_proxy:`**

####  **`no_daemon: install_proxy`**

####  **`add_frontent: install_proxy`**

####  **`add_dev_backend: add_frontent`**

####  **`add_dev_stats: add_dev_backend`**

## web/Makefile
```{r echo=FALSE, warning=FALSE, inlcude=FALSE, results='asis'}
dump_file_cont("makefile", "../images/web/Makefile")
```
::: INFO
>This is [GNU Make Makefile](https://www.gnu.org/software/make/) with usage of [sh](https://www.unix.com/man-page/linux/1/sh/) inside [alpine linux](https://wiki.alpinelinux.org/wiki/Main_Page).
:::

::: CODE_DESCIPTION
### Overwiew

####  **`publish: dummy-file`**

####  **`apache:`**

####  **`php-base: apache`**

####  **`php-add: php-base`**

####  **`enable_php: php-add`**

####  **`dummy-file: enable_php`**
:::

## database/Makefile
```{r echo=FALSE, warning=FALSE, inlcude=FALSE, results='asis'}
dump_file_cont("makefile", "../images/database/Makefile")
```
::: INFO
>This is [GNU Make Makefile](https://www.gnu.org/software/make/) with usage of [sh](https://www.unix.com/man-page/linux/1/sh/) inside [alpine linux](https://wiki.alpinelinux.org/wiki/Main_Page).
:::

::: CODE_DESCIPTION
### Overwiew

####  **`publish: bootstrap db_start db_test db_stop`**

####  **`mysql-server:`**

####  **`mysql-client: mysql-server`**

####  **`mysql-base-init: mysql-client`**

####  **`bootstrap: mysql-base-init`**

####  **`allow_connectivity: bootstrap`**

####  **`.PHONY: db_start db_stop db_test`**

####  **`db_start: allow_connectivity`**

####  **`db_stop:`**

####  **`db_test: db_start`**
:::
