---
title: "Terraform part"
author: "Mateusz Lewicki"
date:  "`r Sys.setlocale('LC_TIME', 'English'); format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: 
    theme: united
    highlight: pygments
    toc: yes
    css: blocks.css
    keep_md: yes
  #  toc_float: yes
  #  number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Puprouse of using Terraform

Terraform by Hashicorp is infrastructure description langauage in HLC format (Hashicorp DSL) used in widely name CI/CD for construction of all needed infrastructure components for application by using principles of infrastructure as code.

## Brief of terrafom in current project
Project consist of 7/8 terraform files (7 as code and 8th for state):

- [variables.tf](../terraform/variables.tf)
- [images.tf](../terraform/images.tf)
- [terraform.tfvars](../terraform/terraform.tfvars)
- [terraform.tfstate](../terraform/terraform.tfstate)
- [outputs.tf](../terraform/outputs.tf)
- [networks.tf](../terraform/networks.tf)
- [main.tf](../terraform/main.tf)

In this project Terraform is used to build "2 tier" infrastructure with loadbalancing in docker.

<center>
```{r,echo=FALSE }
DiagrammeR::mermaid(diagram = '
graph LR;
    A[Client]-->|public| B[HAproxy]
    B-->|private| C[Apache+PHP7]
    C-->E[MySQL]
    B-->|private| D[Apache+PHP7]
    D-->F[MySQL]
    subgraph 10.0.0.32/26
    B
    end
    subgraph 10.0.0.0/26
    C
    E
    end
    subgraph 10.0.0.16/26
    D
    F
    end
')
```
</center>

Terrraform code was split into parts (see above).  
Terraform by default is looking through directory for every Terraform related files.   
Terrafom does not need to have entrypoint file, but it is good practice to have main file.  
Without [backend](https://www.terraform.io/docs/configuration/backend.html) declaration Terraform is using by default `local` provider which means that state file will be created in the same directory

# File description

## main.tf (part of)
```typescript
provider "docker" {
}


resource "docker_container" "LB" {
  image = docker_image.lb.latest
  name  = "LB"
  networks_advanced{
      name=docker_network.public_network.name
  }
  networks_advanced{
      name=docker_network.app_network_1.name
  }
  networks_advanced{
      name=docker_network.app_network_2.name
  }
  ports{
      internal= var.http_port
      external= var.http_port
  }
  ports{
      internal = var.https_port
      external = var.https_port
  }
   ports{
      internal = 1936
      external = 1936
  }
  host{
    host="app1"
    ip=docker_container.apache_1.ip_address
  }
  host{
    host="app2"
    ip=docker_container.apache_2.ip_address
  }
}

[...]

```
::: INFO
>This file consist of [provider](https://www.terraform.io/docs/providers/index.html) 
and [resource](https://www.terraform.io/docs/configuration/resources.html) declaration blocks 
used by [Terraform Configuration Language](https://www.terraform.io/docs/configuration/index.html) 
and [Docker Provider](https://www.terraform.io/docs/providers/docker/index.html)
:::

::: CODE_DESCIPTION
### Overwiew
**main.tf** file is (as the name suggests) the main file of whole infrastructure builded in this project. 
At the top we have `provider` block it is saying that we want to use a docker provider in the latest version (as we don't specified the version)   
Here we have a snippet of on of the **`docker_container`** resource with identifier **`LB`**. This resource is part of Docker provider described above. 
It's built with several fields and block:  

####  **`image = docker_image.lb.latest` - (type: String)  **

>It is a name (or project/name) of the docker image to use. In this case we are referring to `docker_image` resource with `lb` identifier and the `latest`     version. `.latest` can be replaced by `:latest` tag

#### **`name = "LB"` - (type: String)**

>Literal name 

#### **`networks_advanced{name=docker_network.public_network.name }` - (type:block->String)**
 
> Block where we define to which network container should be attached (one block for one network).  
> Inside we have `name` field where we ae using name of network (in this case public) from resource `docker_network` defined in *networks.tf* file

#### **`  ports{ internal= var.http_port external= var.http_port }` - (type:block->Int,Int)**

> Block with definition which ports should be exposed (one block for one ports pair). Here we are using ports from variable `http_port`

#### **`host{ host="app1" ip=docker_container.apache_1.ip_address }`- (type:block->String,String)**  

> Block used for additional `/etc/hosts` entries. Here we are using `ip_address` from `apache_1` the `docker_container` resource 
:::


## images.tf
```typescript
resource "docker_image" "alpine" {
  name = "alpine:latest"
  keep_locally = true
}

resource "docker_image" "web" {
  name = "${var.registry}/${var.web_image_name}"
  keep_locally = true
}

resource "docker_image" "db" {
  name = "${var.registry}/${var.db_image_name}"
  keep_locally = true
}

resource "docker_image" "lb" {
  name = "${var.registry}/${var.lb_image_name}"
  keep_locally = true
}
```
>This file consist of [resource](https://www.terraform.io/docs/configuration/resources.html) declaration blocks 
used by [Docker Provider](https://www.terraform.io/docs/providers/docker/index.html) 

## networks.tf
```typescript
resource "docker_network" "app_network_1" {
  name = "app_network_1"
  internal = true
  ipam_config{
      subnet="10.0.0.0/28"
  }
}

resource "docker_network" "app_network_2" {
  name = "app_network_2"
  internal = true
  ipam_config{
      subnet="10.0.0.16/28"
  }
}
resource "docker_network" "public_network" {
  name = "public_network"
  ipam_config{
      subnet="10.0.0.32/28"
  }
}
```
::: INFO
>This file consist of [resource](https://www.terraform.io/docs/configuration/resources.html) declaration blocks 
used by [Docker Provider](https://www.terraform.io/docs/providers/docker/index.html) 
:::

## variables.tf
```typescript
variable "http_port" {
  type        = string
}

variable "https_port" {
  type        = string
}

variable "db_port" {
  type        = string
}

variable "registry" {
  type        = string
}

variable "db_image_name" {
  type        = string
}
variable "web_image_name" {
  type        = string
}
variable "lb_image_name" {
  type        = string
}
```
::: INFO
>This file consist of [variable](https://www.terraform.io/docs/configuration/variables.html) declaration blocks 
used by [Terraform Configuration Language](https://www.terraform.io/docs/configuration/index.html) 
:::

## outputs.tf
```typescript
output "apache_1_ip_addr" {
  value = docker_container.apache_1.ip_address
}

output "apache_2_ip_addr" {
  value = docker_container.apache_2.ip_address
}
output "LB_ip_addr" {
  value = docker_container.LB.ip_address
}

```
::: INFO
>This file consist of [output](https://www.terraform.io/docs/configuration/outputs.html) declaration blocks 
used by [Terraform Configuration Language](https://www.terraform.io/docs/configuration/index.html) 
:::

## terraform.tfvars
```typescript
  http_port = "80"
  https_port = "443"
  db_port = "3306"
  registry = "localhost:5000"
  web_image_name = "lamp_terr/web"
  db_image_name = "lamp_terr/database"
  lb_image_name = "lamp_terr/loadbalancer"
```
::: INFO
>This file consist of [variable definitions](https://www.terraform.io/docs/configuration/variables.html#variable-definitions-tfvars-files)
:::
